\sectiontitle{Students\\Supervised}

%%%% GRAD STUDENTS

\employer{Valeria Hurtado}
\location{2022 -- Present}
Graduate Student at UW: Searching for Post-AGB stars in WISE and Gaia.\\
{\it Member of PhD committee.}


\employer{Tobin Wainer}
\location{2022 -- Present}
Graduate Student at UW: Looking for variations in stellar flare rates.\\
{\it Member of PhD committee.}


\employer{Anastasios Tzanidakis}
\location{2021 -- Present}
Graduate Student at UW: Searching for rare eclipsing systems with Gaia DR3.\\ 
{\it Member of PhD committee.}


\employer{Guadalupe Tovar Mendoza}
\location{2018 -- Present}
Graduate Student at UW: Properties of flares from Kepler and TESS. First author \\paper \href{https://arxiv.org/abs/2205.05706}{\color{NavyBlue}published.}
NSF GRFP Fellow. {\it Chair of PhD committee.}


\employer{Tyler Gordon}
\location{2018 -- 2023}
Graduate Student at UW: Stellar rotation periods in K2 using Gaussian Processes. \\First author paper \href{https://arxiv.org/abs/2101.07886}{\color{NavyBlue}published.} {\it Member of PhD committee.}

\employer{Jessica Birky}
\location{2019 -- Present}
Graduate Student at UW: NSF GRFP Fellow. Tidal evolution of binaries; \\observations of eclipsing binary stars. Co-mentored with Prof. Rory Barnes (UW). \\{\it Member of PhD committee.}

\employer{Trevor Dorn-Wallenstein}
\location{2017 -- 2020}
Graduate Student at UW: Time domain variability and properties of massive stars from \\surveys including TESS, WISE, and Gaia. Four first-author publications. {\it Member of \\PhD committee.} Now: Carnegie Postdoctoral Fellow.


\employer{Riley Clarke}
\location{2015 -- Present}
Undergraduate at WWU: Studied flare rates from wide binary stars in Kepler. \\Outstanding Poster Award (WWU 2017 Scholars Week). First-author paper \href{https://arxiv.org/abs/1712.04570}{\color{NavyBlue} published.}\\
Now a PhD student at the University of Delaware. Collaborating on flares in LSST. \\  {\it Member of PhD committee.}

\employer{Anna Baum}
\location{2021 -- 2023}
Graduate Student at Lehigh University: Changing inclination eclipsing binaries in \\KELT and TESS. Co-mentored with Prof. Joshua Pepper (Lehigh).



\employer{Spencer Wallace}
\location{2018 -- 2021}
Graduate Student at UW: GKM superflares in TESS Cycle 1 and 2 data. {\it Part of \\student mentoring team.}

\employer{David Fleming}
\location{2018 -- 2020}
Graduate Student at UW: Binary star rotation and tidal evolution. Two first author \\publications. Now in data science industry.



\rule{2in}{0.5pt} %%%%%%%%%%%%%
%%%%% MASTERS AND UNDERGRAD

\employer{Joseph Hand}
\location{2023 -- Present}
Undergraduate at The University of Kansas: Searching for Anomalous lines in\\ APOGEE Spectra. Co-mentored with Howard Isaacson (Berkeley).



\employer{Brian Rogers}
\location{2023 -- Present}
Undergraduate at Queen's University Bellfast: Searching for solar system outliers in LSST.\\ Co-mentored with Dr. Steve Croft (Berkeley) \& Prof. Chris Lintott (Oxford).

\employer{Calder Blackman}
\location{2023 }
Undergraduate at Dartmouth: Discovery Space for ETI in Large Surveys.\\ Co-mentored with Dr. Steve Croft (Berkeley) \& Prof. Chris Lintott (Oxford).


\employer{Ishan Ghosh-Coutinho}
\location{2022 -- Present}
Undergraduate at UW: Exploring the variability of evolved massive stars with \\Gaia and ZTF. Co-mentored with Dr. Trevor Dorn-Wallenstein (Carnegie).



\employer{Donovan Quimby}
\location{2021 -- 2022}
Data Science Masters Student at Georgia Tech: Detecting stellar flicker with TESS.

\employer{Andrew Carr}
\location{2021 -- 2022}
Undergraduate at UW: Building the UW Meteor Camera station.

\employer{Josue Torres-Valdovinos}
\location{2022 -- Present}
Undergraduate at UW: Data reduction and testing with PyKOSMOS. DiRAC Summer \\Research Prize winner (2022).

\employer{Andy Nilipour}
\location{2022-Present}
Undergraduate at Yale: Searching the SETI Ellipsoid with Gaia DR3. Co-mentored \\with Dr. Steve Croft (Berkeley).


\employer{Tien Nguyen}
\location{2021}
Undergraduate at Agnes Scott College: Anomalous lines in APOGEE spectra.\\ Co-mentored with Howard Isaacson (Berkeley).


\employer{Jaide Swanson}
\location{2020 -- 2022}
Undergraduate at UW: Calibrating the ``crowding factor'' for EBs with TESS. \\Co-mentored with Prof. Keaton Bell (CUNY).

\employer{Barbara Cabrales}
\location{2020 -- Present}
Undergraduate at Smith: Searching the SETI Ellipsoid with TESS. Co-mentored with \\Dr. Sofia Sheikh (SETI Inst).


\employer{Anna Zuckerman}
\location{2020 -- 2022}
Undergraduate at Brown: Searching for ``missing transits'' with Kepler. Now a PhD \\student at University of Colorado Boulder. Received NSF GRFP (2022). Co-mentored \\with Dr. Steve Croft (Berkeley).


\employer{Peter Gwartney}
\location{2020 -- 2022}
Undergraduate at UW: Eclipsing binaries in open clusters with TESS. DiRAC Summer \\Research Prize winner (2022). Now a PhD student at University of Alabama.


\employer{Rachel Wong}
\location{2020 -- 2022}
Undergraduate at UW: Rotating stars in open clusters with TESS.

\employer{Karen Warmbein}
\location{2019 -- 2020}
Post-bac researcher: Looking for long-duration dippers in ZTF. Now in industry.


\employer{Hendrik Venter}
\location{2019 -- 2020}
Undergraduate at UW: Exploring {\tt stumpy} for analyzing light curve variability


\employer{Erin Howard}
\location{2019 -- 2021}
Undergraduate at WWU: Eclipsing Binaries in TESS. DREU summer 2021 and summer \\2022 student. NSF GRFP honorable mention. Now research staff with LSST.


\employer{Courtney Klein}
\location{2018 -- 2020}
Undergraduate at UW: Flares in ZTF. Co-mentored with Prof. Eric Bellm (UW). \\Received NSF GRFP (2019). Now a PhD student at UC Irvine.


\employer{Sam Quist}
\location{2018 -- 2019}
Undergraduate at UW: Rotation periods in K2 stars. Completed data science masters\\ at University of British Columbia.

\employer{Zo\"{e} Bell}
\location{2017 -- 2018}
Undergraduate at Harvey Mudd College: First detection of rotation period gap in K2 \\stars.
Received NSF GRFP (2021). Now a PhD student in math at UC Berkeley.

\employer{Michael Puig-Holzman}
\location{2017 -- 2018}
Undergraduate at UW: Measuring rotation periods in K2 stars

\employer{Jamel Adilia}
\location{2017 -- 2018}
Undergraduate at UW: Searching for rotation periods from eclipsing binaries in OGLE.

\employer{Matthew Scoggins}
\location{2018 -- 2020}
Undergraduate at WWU: Flare rate variations in Kepler stars. First-author research note \\\href{https://ui.adsabs.harvard.edu/abs/2019RNAAS...3..137S/abstract}{\color{NavyBlue} published.}
Now a PhD student at Columbia Univerrsity.

\employer{Zachery Laycock}
\location{2016 -- 2018}
Undergraduate at WWU: Stellar activity variations from GALEX

\employer{Jonathan Cornet}
\location{2015 -- 2016}
Undergraduate at WWU: Comparing flare rates between stars in Kepler


\employer{Austin Boeck}
\location{2015 -- 2016}
Undergraduate at WWU: Searching for connection between flares, starspots, and\\ photometric flicker with Kepler.


